Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-08-02 Manuscript/proto-manuscript.tex
Some comments added as todo's in Results and Discussion

\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities.eps}
  \caption{\label{fig:cacl-dens}
    Density profiles of \ce{Ca^{2+}} and \ce{Cl^-} for Lipid14 model with Dang ions
    and with ECC-ions and ECC-lipids model with ECC-ions. }
  \todo{Change the figure so that it contains a membrane background}
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[height=8.5cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \includegraphics[width=9.0cm]{../Fig/ipython_nb/Headgr_OPs_exp-L14-ECCL17.png}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    Headgroup and glycerol backbone order parameters from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{Add acyl chain order parameters, POPC chemical structure} \\
  \todo{We should run a simulation for the system withtout ions with the
    same (or close) temperature as the experimental data. The NMR data is at 300K
    so that would be good. I think that this would be also close enough for the scattering data at 303K.
  }
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities.eps}
  \caption{\label{fig:cacl-dens}
    Density profiles of \ce{Ca^{2+}} and \ce{Cl^-} for Lipid14 model with Dang ions
    and with ECC-ions and ECC-lipids model with ECC-ions. }
  \todo{Change the figure so that it contains a membrane background} \\
  \todo{What are the concentrations (calculated as in NMRlipids II) in this figure?} \\
  \todo{These should be also compared to the results with Åqvist ions, which are shown
    in NMRlipids II. NMRlipids II have results with 350mM and 1000mM. If we have the distributions with
    the same concentrations Åqvist results could be added also in this figure. If not, the
  comparison has to be made some other way.}
\end{figure}
